\bf Title here

### 2020-07-06 paper/paper.Rmd
formation of problem using math notation

Projection pursuit is usually used in conjunction with a tour method called *guided tour*. Tour explores the multivariate data *interactively* via playing a series of projections, that form a *tour path*, like movie frames in real time.  Starting from a randomly generated projection basis, projection pursuit searches for a target basis with higher index value and guided tour interpolates geodesically between the initial basis and the target basis.  This series of bases forms a tour path and the projection of the data on these bases is played in real time.  This search-and-interpolate process is repeated until no basis can be found with higher index value. Modified from @buja2005computational, Figure \ref{tour-path} vividly depicts the tour path in guided tour. Guided tour, along with other types of tour, has been implemented in the *tourr* package in R, available on the Comprehensive R Archive Network at [https://cran.r-project.org/web/packages/tourr/](https://cran.r-project.org/web/packages/tourr/) [@wickham2011tourrpackage].

@@

>>>>

Projection pursuit is usually used in conjunction with a tour method called *guided tour*. Tour explores the multivariate data *interactively* via playing a series of projections, that form a *tour path* and guided tour uses the path that is geodesically the shortest. Details of the mathematical construction of a tour path can be found in @buja2005computational. Modified from @buja2005computational, Figure \ref{tour-path} vividly depicts the tour path in guided tour. Guided tour, along with other types of tour, has been implemented in the *tourr* package in R, available on the Comprehensive R Archive Network at [https://cran.r-project.org/web/packages/tourr/](https://cran.r-project.org/web/packages/tourr/) [@wickham2011tourrpackage].

@@

Now we formulate the problem in mathmetical notation. Projection pursuit finds the projection basis $A^J = [\mathbf{a}_1, \cdots, \mathbf{a}_d]$, where $\mathbf{a}_i$ is a $p \times 1$ vector, satisfying the following optimisation problem:

\begin{align}
I &= \arg \max_{A \in \mathcal{A}^{p \times d}} f(A) \\
s.t. & \mathcal{A} = \{ \forall \mathbf{a}_i \in A: \lVert \mathbf{a}_i \rVert = 1 \}
\end{align}

via an iterative search: $\{A^1, A^2, \cdots \cdots A^J\}$. Guided tour interpolates geodesically between each basis found by projection pursuit $A^j$ to form a tour path: $$\{A^1, A^1_1, A^1_2,\cdots, A^1_{k_1}, A^2, A^2_1, A^2_2, \cdots A^2_{k_2}, A^3, \cdots, A^{J-1}, A^{J-1}_{1}, \cdots A^{J-1}_{k_m} ,A^J  \}$$

### 2020-07-06 paper/paper.tex
formation of problem using math notation

Projection pursuit is usually used in conjunction with a tour method
called \emph{guided tour}. Tour explores the multivariate data
\emph{interactively} via playing a series of projections, that form a
\emph{tour path}, like movie frames in real time. Starting from a
randomly generated projection basis, projection pursuit searches for a
target basis with higher index value and guided tour interpolates
geodesically between the initial basis and the target basis. This series
of bases forms a tour path and the projection of the data on these bases
is played in real time. This search-and-interpolate process is repeated
until no basis can be found with higher index value. Modified from
\citet{buja2005computational}, Figure \ref{tour-path} vividly depicts
the tour path in guided tour. Guided tour, along with other types of
tour, has been implemented in the \emph{tourr} package in R, available
on the Comprehensive R Archive Network at
\url{https://cran.r-project.org/web/packages/tourr/}
\citep{wickham2011tourrpackage}.

@@

>>>>

Projection pursuit is usually used in conjunction with a tour method
called \emph{guided tour}. Tour explores the multivariate data
\emph{interactively} via playing a series of projections, that form a
\emph{tour path} and guided tour uses the path that is geodesically the
shortest. Details of the mathematical construction of a tour path can be
found in \citet{buja2005computational}. Modified from
\citet{buja2005computational}, Figure \ref{tour-path} vividly depicts
the tour path in guided tour. Guided tour, along with other types of
tour, has been implemented in the \emph{tourr} package in R, available
on the Comprehensive R Archive Network at
\url{https://cran.r-project.org/web/packages/tourr/}
\citep{wickham2011tourrpackage}.

@@

Now we formulate the problem in mathmetical notation. Projection pursuit
finds the projection basis
\(A^J = [\mathbf{a}_1, \cdots, \mathbf{a}_d]\), where \(\mathbf{a}_i\)
is a \(p \times 1\) vector, satisfying the following optimisation
problem:

\begin{align}
I &= \arg \max_{A \in \mathcal{A}^{p \times d}} f(A) \\
s.t. & \mathcal{A} = \{ \forall \mathbf{a}_i \in A: \lVert \mathbf{a}_i \rVert = 1 \}
\end{align}

via an iterative search: \(\{A^1, A^2, \cdots \cdots A^J\}\). Guided
tour interpolates geodesically between each basis found by projection
pursuit \(A^j\) to form a tour path:
\[\{A^1, A^1_1, A^1_2,\cdots, A^1_{k_1}, A^2, A^2_1, A^2_2, \cdots A^2_{k_2}, A^3, \cdots, A^{J-1}, A^{J-1}_{1}, \cdots A^{J-1}_{k_m} ,A^J  \}\]
